---
title: "Caffeinemania"
subtitle: "STATS 220 Semester One 2025"
author: "Tevita Pepa"
output: html_fragment
code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
library(ggplot2)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRe8AES_4cuUoNl9gLj1TW_NxLy-Oh0fDgLq1NIwMZlylDWUQBm3XRfVfcXzmANEWFshMGnNd36NZFd/pub?output=csv") %>% 
  rename(drink_brand = 2,
         drink_size = 3,
         drink_reason = 4,
         sugar_free = 5,
         prior_drinks = 6,
         drink_symptoms = 7,
         energy_scale = 8)

num_yes <- sum(logged_data$sugar_free == "Yes")
num_no <- sum(logged_data$sugar_free == "No")

musashi_count <- sum(logged_data$drink_brand == "Musashi")

most_common <- logged_data %>%
  count(drink_brand,sort = TRUE)%>%
  slice(1)
```

```{css echo= FALSE}
h2{
  font-family: 'Reactive Anchor', sans-serif;
  color: #b7f791;
  background-color: #70b04a;
  font-size: 40px;
  padding: 20px;
  font-weight: normal;
  text-shadow: 1px 1px 0px black;
}
h3{
   font-family: 'Reactive Anchor', sans-serif;
  color: #b7f791;
  background-color: #70b04a;
  font-size: 35px;
  padding: 10px;
  font-weight: normal;
  text-shadow: 1px 1px 0px black;
}
body{
  font-size: 12pt;
  font-family: 'Avenir Next', sans-serif;
  color:black;
  background:linear-gradient(90deg, #b7f791, #87e84e);
  padding: 10px;


```

## Impact of Energy Drink brand/sugar-free options on energy levels

In this study, examine the impact of energy drinks of varying brands and sugar-free options to explain whether they had an impact on my energy levels. As someone who regularly has energy drinks of all kinds for different reasons whether I felt tired from studying, needed a boost for sports or the gym or just out of habit I decided include those reasons within my dataset to provide extra content. To make my data more robust, I also included whether or not I had symptoms after drinking in my logging form and the can sizes. 

The bar charts illustrate my energy levels on a scale of 1 (no effect) to 10 (too much). 

### Sugar-Free Plot
The colours in graph illustrate the proportion of scores that were sugar-free (blue) or full-sugar (red) energy drinks.

On average, I had `r num_yes` sugar-free drinks. 
Whereas the number of sugared energy drinks I had was `r num_no`.
```{r}
ggplot(data = logged_data) +
    geom_bar(aes(x = energy_scale, fill = sugar_free))
```

### Brand Plot
Here is my bar chart for my energy scores across energy drink brands.The colours in this graph represent the proportion of socres linked to specific brands. 

```{r}
ggplot(data = logged_data) +
  geom_bar(aes(x = energy_scale, fill = drink_brand))
```

My favourite energy drink brand was `r most_common$drink_brand[1]` where I had `r most_common$n[1]`
