---
title: "Caffeinemania"
subtitle: "STATS 220 Semester One 2025"
author: "Tevita Pepa"
output: html_fragment
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
library(ggplot2)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRe8AES_4cuUoNl9gLj1TW_NxLy-Oh0fDgLq1NIwMZlylDWUQBm3XRfVfcXzmANEWFshMGnNd36NZFd/pub?output=csv") %>% 
  rename(drink_brand = 2,
         drink_size = 3,
         drink_reason = 4,
         sugar_free = 5,
         prior_drinks = 6,
         drink_symptoms = 7,
         energy_scale = 8)
how_many <- length(logged_data$energy_scale)

num_yes <- sum(logged_data$sugar_free == "Yes")
num_no <- sum(logged_data$sugar_free == "No")

most_common <- logged_data %>%
  count(drink_brand,sort = TRUE)%>%
  slice(1)

```

```{css echo= FALSE}
h2{
  font-family: 'Reactive Anchor', sans-serif;
  color: #b7f791;
  background-color: #70b04a;
  font-size: 40px;
  padding: 20px;
  font-weight: normal;
  text-shadow: 1px 1px 0px black;
}
h3{
   font-family: 'Reactive Anchor', sans-serif;
  color: #b7f791;
  background-color: #70b04a;
  font-size: 35px;
  padding: 10px;
  font-weight: normal;
  text-shadow: 1px 1px 0px black;
}
body{
  font-size: 12pt;
  font-family: 'Avenir Next', sans-serif;
  color:black;
  background:linear-gradient(90deg, #b7f791, #87e84e);
  padding: 10px;
}
```

## Impact of Energy Drink brand/sugar-free options on energy levels

In this study, I examined the impact of energy drinks of varying brands and sugar-free options to explain whether they had an impact on my energy levels.

The bar charts illustrate my energy levels on a scale of 1 (no effect) to 10 (too much). 

### Sugar-Free Plot
The colours in graph illustrate the proportion of scores that were sugar-free (blue) or full-sugar (red) energy drinks.


On average, I had `r num_yes` sugar-free drinks. 
Whereas the number of sugared energy drinks I had was `r num_no`.

```{r}
ggplot(data = logged_data) +
    geom_bar(aes(x = energy_scale, fill = sugar_free)) +
  labs(title = "Energy Levels! Sugar-free vs Sugared",
       subtitle = "Comparing the distribution of sugar-free/sugared energy drinks across energy levels",
       caption = "Source: Caffeinemania",
       x = "Energy Scale (1 = no effect, 10 = too much",
       y = "Count")
```


**Note: Can see that the only 10 scores are sugared drinks!**

### Brand Plot
Here is my bar chart for my energy scores across energy drink brands. The colours in this graph represent the proportion of socres linked to specific brands. 

Out of the `r how_many` energy drinks I had, `r most_common$n[1]` of them were `r most_common$drink_brand[1]`.

```{r}
ggplot(data = logged_data) +
  geom_bar(aes(x = energy_scale, fill = drink_brand))+
  labs(title = "Energy Levels Brands Warfare",
       subtitle = "Comparing the distribution of energy drink brand across energy levels",
       caption = "Source: Caffeinemania",
       x = "Energy Scale (1 = no effect, 10 = too much",
       y = "Count")
```


**Note: Can see that the only 10 scores are drinks from V and Rockstar!**
