---
title: Caffeinemania
output: html_fragment
---
```{css, echo=FALSE}

body {
  font-family: 'Caviar Dreams',sans-serif;
  font-weight: bold;
  color:black;
  background: linear-gradient(90deg, #d6ffbe, #ceffb1);
  padding: 10px;
  font-size: 14px;
  
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)
library(ggplot2)
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRe8AES_4cuUoNl9gLj1TW_NxLy-Oh0fDgLq1NIwMZlylDWUQBm3XRfVfcXzmANEWFshMGnNd36NZFd/pub?output=csv") %>% 
  rename(drink_brand = 2,
         drink_size = 3,
         drink_reason = 4,
         sugar_free = 5,
         prior_drinks = 6,
         drink_symptoms = 7,
         energy_scale = 8)

num_yes <- sum(logged_data$sugar_free == "Yes")
num_no <- sum(logged_data$sugar_free == "No")

musashi_count <- sum(logged_data$drink_brand == "Musashi")

most_common <- logged_data %>%
  count(drink_brand,sort = TRUE)%>%
  slice(1)
```



## Energy Levels after drinking energy drinks (Sugar-Free vs Sugar – Brand vs Brand)

In this study, I decided to analyse and compare energy drink brands and their sugar-free options. The goal of the study was to see if there was a connection between brands/sugar-free energy drinks and the impact that it had on my energy levels after drinking them. Considering I regularly drink energy drinks of all kinds for multiple purposes (tiredness, routine and sports), I also decided to include those reasons within my dataset to provide surrounding context and see if there was an effect there as well. To make my data more robust, I also included whether or not I had symptoms after drinking in my logging form.

The bar charts show my energy levels on a scale of 1-10 with 10 being too high and 1 being too low that I didn't feel any change. The colours of the charts represent the proportion of those scores were from which energy drink brand or were a sugar/sugar-free option.

here is the bar chart recording the proportion of my energy scores with blue being sugar-free and red being sugared energy drinks.

the mean number of energy drinks I had that were sugar-free was `r num_yes` ! Whereas the number of sugared energy drinks I had was `r num_no`.

```{r}
ggplot(data = logged_data) +
    geom_bar(aes(x = energy_scale, fill = sugar_free))
```

Here is my bar chart for my energy scores across energy drink brands.

```{r}
ggplot(data = logged_data) +
  geom_bar(aes(x = energy_scale, fill = drink_brand))
```

My favourite energy drink brand was `r most_common$drink_brand[1]` where I had `r most_common$n[1]` this is tied with V.
